Final assignment presentation

### 2022-12-01 summary_final_assingment.Rmd
final_push

---
title: "draft_final_assignment"
author: "Andrew Wells"
date: "11/18/2022"
output: 
  html_document:
    toc: TRUE
    theme: cosmo
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
library(plotly)
```

@@

```{r }
df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")
head(df, 5)
```

@@

@@

textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300, color = c("green","orange","grey"))

@@

p
ggplotly(p)
```

@@

j
ggplotly(j)
```

@@

@@

## Conclusion

>>>>

---
title: "Final assignment presentation"
author: "Alexander Kraess, Andrew Wells, Julian Kath & Lorenzo Gini"
date: "11/18/2022"
output: 
  prettydoc::html_pretty:
    theme: hpstr
    hightlight: github
    toc: TRUE
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmltools)
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
library(plotly)
library(reticulate)
library(igraph)
library(rjson)
library(visNetwork)
```

@@

```{r }
df <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_11_28.csv")
df_cosp <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/cosponsors_sponsors.csv")
df_bills <- read_csv("data\\old_data\\all_bills.csv")
head(df, 5)
```

@@

## Policy fields

```{r}
fromJSON(file = "slides\\plots\\polar_line_plot") %>% plotly::as_widget()
```

@@

textplot_wordcloud(dfmatCon, comparison = TRUE, max_words = 300,
                   color = c("blue", "red"))

@@

p <- ggplotly(p)
p
```

@@

j <- ggplotly(j)
j
```

@@

# Network graph of 116 House members

```{r}
df_labels <- df_cosp %>% 
  inner_join(
    df, 
    by = c("number"= "bill number")
  ) %>% 
  inner_join(
    df_bills %>% select(number, originChamber),
    by = 'number'
  ) %>% 
  filter(session == 116, originChamber == 'House') %>% 
  mutate(
    cosponsor_name = str_replace_all(cosponsor_name, '\\w\\.\\s', ''),
    cosponsor_name = str_replace_all(tolower(cosponsor_name), " ", "_"))

df_labels %>% 
  group_by(number) %>% 
  summarize(cosps = paste(cosponsor_name, collapse = " ")) -> df_grouped

corpus(df_grouped$cosps) %>% 
  tokens() %>% 
  fcm() %>% 
  as.matrix() %>% 
  graph_from_adjacency_matrix(mode = "undirected", weighted = T) %>% 
  toVisNetworkData() -> visn

visn$edges$value <- visn$edges$weight

edges <- data.frame(visn$edges) %>% 
  filter(weight > 25)
nodes <- data.frame(visn$nodes) %>% 
  left_join(df_labels %>% select(cosponsor_name, cosponsor_party) %>% distinct(), by = c('label' = 'cosponsor_name')) %>% 
  filter(!duplicated(label)) %>% 
  rename('group' = 'cosponsor_party') %>% 
  mutate(color.background = if_else(group == "R",  "darkred", "darkblue"),
         shadow = T,
         font.color = 'black',
         borderWidth = 2) %>% 
  filter(label %in% edges$from | label %in% edges$to) %>% 
  mutate(label = str_replace_all(label, '_',  ' ') %>% tools::toTitleCase(),
         title = label)

network <- visNetwork(nodes, edges) %>% 
  visNodes(color = list(border = "darkgrey", 
                        borderWidth = 2,
                        highlight = list(border = 'darkgrey', background = 'orange'))
           ) %>% 
  visEdges(color = list(color = '#d3d3d3', highlight = 'orange')) %>% 
  visPhysics(maxVelocity = 3)

network
```

@@

```{r}
umap <- read.csv('data\\umap_projection_data.csv')

umap %>% 
  ggplot(aes(x, y, color = cosponsor_D_perc,
             text = paste('Title:' , title, 
                          '<br>Policy Area: ', policyarea, 
                          '<br>Session: ', session, 
                          '<br>Topic: ', cluster))) +  
  geom_point() + 
  scale_color_gradient2(midpoint = .5, name = "Democrat share") + 
  theme_minimal() + 
  labs(x = '', y = '', title = "UMAP Projection of US Congress bill summaries 115-117") +
  theme(panel.background = element_rect(fill='#fbfbfb', colour='#fbfbfb')) -> p

ggp <- ggplotly(p)

ggp
```

## Conclusion
- In general the legilsation appears quite similar, with exceptions limited to specific policy areas and topics
- Democratic and Republican cooperation across the different congress sessions is highly dependent on the policy area and topic of the bill
- There are some key actors that enable working across the aisle and are known for bipartisan collaboration
